\SW: Crowd-sourcing the Discovery of Gravitational Lenses

### 2015-04-13 doc/sw-system.tex
Added fitsjs reference, including doi. Fixes #119
fix js typo

For the more interesting subjects, the CI offers two features that  enable
further investigation of the subjects. The first is the ``Quick Dashboard'' (QD)
a more advanced image viewer. This allows the viewer to compare three different
contrast and colour balance settings, to help bring out subtle features, and to
pan and zoom in on interesting regions of the image to assess small features.
Markers can be placed in the Quick Dashboard just the same as in the main CI
image viewer. The second is a link to that subject's page in the project
discussion forum, \texttt{http://talk.spacewarps.org} (known as ``Talk''). Here,
volunteers can discuss the features they have seen either before they submit
their classification, or after, if they ``favorite'' the subject. There is no
``back'' button: each volunteer may only classify a given subject once. However,
the presence of an option to see what others think about any given subject
before submitting your own classification means that the classifications may not
be strictly independent; the advantage of this system is that volunteers can
learn from others what constitutes a good lens candidate. This is not, however,
the primary educational resource; we describe the explicit training that we
provide for the volunteers in the next section. The FITS images of the subject can be further explored with Zooniverse ``Dashboard Tools,'' using a more powerful image viewer that enables dynamic variation of the colour balance and contrast (stretch), and for any given view to be shared via unique URL back to Talk.

@@

When all the subjects had either been retired, or classified around 10 times
or more, the web app was paused and reconfigured for \StageTwo. The sample of
subjects classified during \StageTwo was selected to be all those that passed
the detection threshold ($\pr(\LENS|C,T) > 0.95$) at \StageOne. These were
classified for one week, with no retirement but a maximum classification
number of 50 each. The number of subjects at \StageTwo was small enough that we
did not need to retire any: instead, we simply collected classifications for a
fixed period of time (about 4 weeks). Without the time pressure motivating the
online analysis, we implemented an ``offline'' version of the analysis that
performs a joint inference of all agent confusion matrix elements and subject
probabilities simultaneously, for comparison. We describe how this differs
from the online analysis in the appendix.

@@

@@

In this section we present our findings about the performance of the  \sw
system, in terms of the information  contributed by the crowd in
\Sref{sec:results:crowd}, and the overall classifications of the training set
that they made.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}
\centering\includegraphics[width=0.9\linewidth]{sw-system-figs/all_skill_contribution_experience_education.png}
\caption{Key properties and contributions of the \sw crowd. Plotted are the
1-D and 2-D marginalized distributions for the logarithms of the
properties of the agents described in the text. The \StageOne agents are shown
in blue, the \StageTwo agents in orange.}
\label{fig:crowd:cornerplot}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

We define the following properties of the crowd, as characterised by their
agents, and plot the distributions of their logarithms in
\Fref{fig:crowd:cornerplot}.
%
\begin{description}
%
\item{\noindent\bf ``Effort:''} The number of test images, $\effort$, classified by a
volunteer. In \StageOne, the mean effort per agent was 263; in the shorter \StageTwo it was 81.
%
\item{\noindent\bf ``Experience:''} The number of training images, $\experience$,
classified by a volunteer. In \StageOne, the mean experience per agent was 29;
in \StageTwo (where the training image fequency was set higher) it was 34.
%
\item{\noindent\bf ``Skill:''} The expectation value of the information gain,
$\skill$
should  the next subject classified have lens probability 0.5
(\Aref{appendix:swap}),  in bits. Random classifiers have $\skill = 0.0$,
perfect classifiers have $\skill = 1.0$. All agents start with $\skill = 0.0$;
this increases as training subjects are classified, and the agent's estimates
of its confusion matrix elements improve. In \StageOne, the mean skill per agent
was 0.04 bits; in  \StageTwo it was 0.05.
%
\item{\noindent\bf ``Contribution:''} The integrated skill over a volunteer's test
subject classification history, and represents the total  contribution to the
project that volunteer (see the appendix for more discussion of this
quantity). In \StageOne, the mean contribution per agent was 34.9 bits; in
\StageTwo it was 33.5.
%
\item{\noindent\bf ``Information:''} The total information $\information$ generated by
the  agent during the volunteer's classification activity. This quantity
depends on the value of each subject's lens probability when that subject was
presented to the volunteer (\Aref{appendix:swap}), and so there is an element
of luck involved with this quantity: if you never see a high probability
subject, it's hard to generate a large amount of information. You make your
own luck by classifying more subjects.
%
\end{description}

The leftmost column of \Fref{fig:crowd:cornerplot} shows how the last four of
these properties depends on the effort expended by the volunteers. We see that
experience is strongly correlated with effort (as training images are
presented throughout each stage, albeit at decreasing frequency), and that
this is also true for skill. In the second row of \Fref{fig:crowd:cornerplot}
we see that while skills of greater than 0.1 can be attained after just a few
training images, most agents of such low experience have significantly lower
skill. The volunteers in question only classify a few subjects before leaving.
However, at high values of experience and effort, the skill is \emph{always
high}. There seem to be very few agents logging large numbers of
classifications at low skill (although there are one or two exceptions): almost
all high effort ``super-users'' have high skill. These two properties are
reflected in both the contributions these volunteers make (third row) and the
information they generate (fourth row).

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}
\centering\includegraphics[width=0.9\linewidth]{sw-system-figs/crowd_contrib_cumul.png}
\caption{Narrow cumulative distributions of the contributions made by the
agents: for example, 90\% of the \StageTwo contributions were made by the
highest contributing  7\% of the crowd. The \StageOne agents are shown in blue,
the \StageTwo agents in orange. ``Experienced volunteers'' classified 10 or more
training subjects.}
\label{fig:crowd:cumulplot}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\Fref{fig:crowd:cornerplot} shows the \sw crowd to have quite broad
distributions of logarithmic effort, skill, and contribution. To better
quantify the contributions made by the volunteers, we show their cumulative
distribution on a linear scale in \Fref{fig:crowd:cumulplot}. This plot shows
clearly the importance of the hardest-working, most active volunteers: at
\StageOne,  1.0\% of the volunteers -- 375 people -- made 90\% of the
contribution.  At \StageTwo, where it was not possible to make as
many classifications before running out of subjects, 7.2\% of the volunteers
-- 141 people -- made 90\% of the contribution.

However, it is not the case that only these small groups were capable of
making this large contribution.
% : 9118 volunteers were ``experienced'' in that
% they had all classified at least 10 training images; the 375 highest
% contributing volunteers make up just 4\% of this experienced volunteer pool.
The cumulative distribution of agent skill is shown in
\Fref{fig:crowd:cumulskillplot}: these distributions are significantly broader
than the corresponding distributions of agent contribution in
\Fref{fig:crowd:cumulplot}. The most skilled 20\% of agents possess only  79\%
of the skill at \StageOne, and 77\% at \StageTwo. The inexperienced volunteers
also possess a significant fraction of the skill: the most skillful 20\% of
experienced volunteers (1824 people)  possess just 43\% of the total skill.
The level of contribution made at \sw by experienced volunteers is largely a
matter of choice (or perhaps, availability of time!).

@@

How fast does the \sw crowd classify subjects? Each agent records the timestamp
of each classification its volunteer makes; by measuring the time lags between
successive classifications we can make estimates of the crowd's classification
and contribution speed. We plot these two quantities for both \StageOne and \StageTwo in \Fref{fig:results:speed}, normalizing the speed and time axes to the
respective totals. The fractional classification rates in each stage of the survey fall off in approximately the same way, despite the factor of nearly 20 difference in crowd size. \StageOne (consisting of $\sim430,000$ subjects) was completed in around 5000 hours (by some 37,000 participants), with classification rates in the first few days averaging at $\sim10^4$ per hour, stimulated by various forms of advertising (press releases, and emails to registered Zooniverse users). The asymptotic classification rate was $\sim10^3$ per hour. The average skill was found to be approximately constant over the lifetime of \StageOne, leading to a contribution rate that tracks closely the classification rate. (A 10\% increase in average skill was seen over the first 40 days, and a decrease of the same amount in the last 40 days -- not enough to cause a significant difference between classification and contribution rate behavior, but perhaps reflecting a learning period at the start and a decrease in participation late on.) \StageTwo (3700 subjects) was completed in around 600 hours by around 2000 participants, with classification rates starting at $~\sim2000$ per hour and decaying to $\sim100$ per hour.

@@

We now quantify the performance of the \sw system in terms of the recovery of
the training set images. At \StageOne, this set contains around 5712 simulated
lenses, and 450 duds; at \StageTwo, we used 152 simulated lenses and 201 duds.
\Fref{fig:results:sample:roc} shows receiver operating characteristic (ROC)
curves for CFHTLS \StageOne and \StageTwo. These plots show the true positive
rate (TPR), the number of sims correctly detected divided by the total number of
sims in the training set, and the false positive rate (FPR), the number of duds
incorrectly detected  divided by total number of duds in the training set, both
for a given sample of detections defined by a particular probability threshold,
which varies along the curves.  In both stages, these curves show that true
positive rates of  around 90\% were achieved, at very low false positive rates.
For comparison we show the results of an analysis where the classifications of
training images were ignored, and none of the agents allowed to learn: they were
instead assigned initial values of their confusion matrices of 0.75 for each
element, which then remained constant. This emulates a very simple unweighted
voting scheme, where all classifications are treated equally. In this case, the
TPR remains under 80\% in \StageOne and 60\% in \StageTwo, thus quantifying  the
benefit of including training images and allowing the agents to learn. The
choice of initial confusion matrix is not very important: the same 0.75 initial
values applied to normal, learning agents results in a slightly lower TPR than
the default case, indicating that initializing the system less conservatively
results in slightly worse performance.

The dot-dashed curves show the impact of the offline analysis. At \StageOne the
results are very similar to the online version that was actually run (solid
line). However, at \StageTwo there is marginal evidence of there being greater
benefit to doing the analysis offline. Over 85\% TPR is achieved at zero FPR
in the offline analysis , while if one is willing to accept a false positive
rate of 5\%, the true positive rate rises to over 95\%, showing that some of
the sims that were missed in the online analysis may be being recovered by
doing the analysis offline. The same is true at \StageOne, but to a lower
degree. Assuming Poisson statistics for the fluctuations in the numbers of
recovered lenses, the uncertainty in the measured \StageTwo TPR values is around
8\%, but the online and offline samples are highly correlated, such that the
uncertainty on the difference between the ROC curves is somewhat less than
this. Still, a larger validation set is needed to test these algorithmic
choices more rigorously. At \StageOne, high TPR can be measured to better than
1\%.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}
\begin{minipage}{0.45\linewidth}
  \centering\includegraphics[width=\linewidth]{sw-system-figs/stage1_ROC.png}
\end{minipage}\hfill
\begin{minipage}{0.45\linewidth}
  \centering\includegraphics[width=\linewidth]{sw-system-figs/stage2_ROC.png}
\end{minipage}
\caption{Receiver operating characteristic curves for the \sw system, using
the CFHTLS training set. Left: \StageOne, right: \StageTwo.}
\label{fig:results:sample:roc}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

Adopting the online \StageOne analysis, and the offline \StageTwo analysis, we
show in \Fref{fig:results:sample:CP} a plot of the more familiar (to
astronomers) quantities completeness versus purity in
the two stages. As in \Fref{fig:results:sample:roc}, the detection threshold
varies along the curves. Completeness is defined as the number of correctly
detected sims divided by the total number of sims in the training set, while
purity is the number of correct detections divided by the total number of
detections.\footnote{The completeness is equivalent to the TPR and is also
known elsewhere as the ``recall.''  The purity is also known as the
``precision.''} If the training set samples from the same systems as the test
set, then the completeness of the training set will be equivalent to the
completeness of the test set. The purity depends on the proportion of sims to
duds, and so the purity of the test set must be approximated by rescaling the
training set to the expected proportion of lens systems to not-lens systems in
the survey. First we compute the expected number of false positives by
multiplying the FPR by the expected number of non-lenses in the survey. Then
we multiply the TPR by the expected number of lenses in the survey, to get the
expected number of true positives. The sum of the true positives and the false
positives gives the expected sample size; dividing the expected number of true
positives by this sample size gives the purity. Note that the completeness is
invariant to this transformation.

The \StageOne curves are truncated by the retirement of subjects in this phase,
which sets the minimum size of this sample. We see from the solid blue curve
that over 90\% completeness was reached, albeit in a sample with around 20\%
purity. To investigate the completeness to the three different types of lens
in the training set, we repeat the same procedure, only now we consider only
the detections of a certain kind of lens and of the non-lenses in the training
set. We estimate the expected number of lenses and non-lens false positives by
dividing the lens and dud sets into equal fractions.

The lensed quasar part of the training set yielded the highest
completeness, suggesting that these were the easiest sims to spot. The lensed
galaxies were recovered at understandably lowest completeness, although the
wider image separation  lensing clusters were not very different. At \StageTwo,
where no retirement was carried out, it was possible to reach 100\% purity:
indeed, the knee of the curve is at just under 90\% completeness. However, the
purity decreases rapidly if higher completeness than this is sought.
Interestingly, the lensing clusters can be seen to pose problems for the
system, with its curve turning over at just 60\% completeness.

The optimal sample in this simulated lens search experiment would have been
constructed with a threshold value of $\pr(\LENS|C,T) > 0.47$. At 100\% purity
and 89\% completeness, it would have contained around 89 lens candidates.
% TP + FN ~ 2e-4 * 430000 ~ 100 ~ TP/C ; so TP ~ 89 candidates

@@

We investigated the source of the incompleteness and impurity visible in
\Fref{fig:results:sample:CP}, by examining the \StageTwo false negatives and
false positives, and their behaviour as they are classified using the online
analysis trajectory plots introduced in \Sref{sec:swap}
(\Fref{fig:swap:subject-trajectories}).
\Fref{fig:discuss:performance:trajectories} shows 2 example simulated lenses
that were missed ($\pr(\LENS|C,T) < 10^{-5}$) by the \sw system, and 2 example
non-lenses that were incorrectly flagged as candidates ($\pr(\LENS|C,T) >
0.95$) by the \sw system. While the final \StageTwo analysis was done offline,
these trajectory plots still serve to illustrate the approximate
classification histories of the subjects.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{table*}
\begin{center}
\caption{Total crowd and subject sample properties from the CFHTLS project.}
\label{tab:crowd:contributions}
\begin{tabular}{cccccccc}
  \hline
  \hline {Stage} & Subjects & Contribution                          & Agents & Skill      & Classifications          & Candidates & Information \\
                 & $\Ns$    & $\sum_k^{\Nv} \contribution_k$ (bits) & $\Nv$  & $\sum_k^{\Nv} \skill_k$ (bits) & $\sum_k^{\Nv} \thiseffort$ & $\Ncands$  & $\sum_j^{\Ns}\sum_k^{\Nv} \information_{j,k}$ (bits) \\
  \hline
            1    & $427064$ & $1292016.3$ & $36982$ & $1471.9$ & $10802125$ & $3368$ & $91122.6$ \\
            2    & $3679$   &   $21895.8$ &  $1964$ &  $102.4$ &   $224745$ &   $90$ &  $1640.4$ \\
  \hline \hline
\end{tabular}
\medskip\\
\end{center}
\end{table*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

Finally, we comment on the size of the first \sw crowd, and how the system
might be scaled up for future surveys. In \Sref{sec:results:crowd} and
\Tref{tab:crowd:contributions}, a rough picture emerged for the \sw crowd of
it containing a few $10^4$ volunteers, with a few $10^3$ achieving
considerable skill, and a few $10^2$ having the time to make a significant
contribution. Slightly more quantitively, we might note that  the total skill
of the crowd, computed by summing the skill of all the agents, is a measure of
the effective crowd size, in the sense that a crowd of perfect classifiers
would be of this size. By this measure,the \StageOne crowd was equivalent to a
team of 1470 perfect classifiers, while the \StageTwo crowd was equivalent to a
team of 102 perfect classifiers. With this same crowd, we can see that surveys
providing a few $10^4$ subjects would be completed quickly, if the high
contribution rate of the current crowd were to be repeated.

>>>>

For the more interesting subjects, the CI offers two features that  enable
further investigation of the subjects. The first is the ``Quick Dashboard''
(QD) a more advanced image viewer. This allows the viewer to compare three
different contrast and colour balance settings, to help bring out subtle
features, and to pan and zoom in on interesting regions of the image to assess
small features. Markers can be placed in the Quick Dashboard just the same as
in the main CI image viewer. The second is a link to that subject's page in
the project discussion forum, \texttt{http://talk.spacewarps.org} (known as
``Talk''). Here, volunteers can discuss the features they have seen either
before they submit their classification, or after, if they ``favorite'' the
subject. There is no ``back'' button: each volunteer may only classify a given
subject once. However, the presence of an option to see what others think
about any given subject before submitting your own classification means that
the classifications may not be strictly independent; the advantage of this
system is that volunteers can learn from others what constitutes a good lens
candidate. This is not, however, the primary educational resource; we describe
the explicit training that we provide for the volunteers in the next section.
The FITS images of the subject can be further explored with Zooniverse
``Dashboard Tools,'' using a more powerful image viewer that enables dynamic
variation of the colour balance and contrast (stretch), and for any given view
to be shared via unique URL back to Talk. The FITS image viewing in both the
Quick Dashboard and the Dashboard Tools are enabled by the javascript library
\fitsjs \citep{fitsjs}.

@@

When all the subjects had either been retired, or classified around 10 times
or more, the web app was paused and reconfigured for \StageTwo. The sample of
subjects classified during \StageTwo was selected to be all those that passed
the detection threshold ($\pr(\LENS|C,T) > 0.95$) at \StageOne. These were
classified for one week, with no retirement but a maximum classification
number of 50 each. The number of subjects at \StageTwo was small enough that we
did not need to retire any: instead, we simply collected classifications for a
fixed period of time (about 4 weeks). Without the time pressure motivating the
probabilities simultaneously, for comparison. We describe how this differs
from the online analysis in the appendix.

@@

In this section we present our findings about the performance of the \SW system,
in terms of the information  contributed by the crowd in
\Sref{sec:results:crowd}, the speed of the system, and the overall
classifications of the training set that they made.

@@

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}
\centering\includegraphics[width=0.9\linewidth]{sw-system-figs/all_skill_contribution_experience_education.png}
\caption{Key properties and contributions of the \SW crowd. Plotted are the 1-D
and 2-D smoothed marginalized distributions for  the logarithms of the
properties of the agents described in the text. The  \StageOne agents are shown
in blue, the \StageTwo agents in orange: the  smoothing scale for the \StageTwo
curves was set slightly higher to counter the  higher shot noise. The contours
contain 68\%, 95\% and 99\% of the distributions.}
\label{fig:crowd:cornerplot}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

We define the following properties of the crowd, as characterised by their
agents, and plot their distributions in
\Fref{fig:crowd:cornerplot}.
%
\begin{description}
%
\item{\noindent\bf ``Effort:''} The number of test images, $\effort$, classified
by a volunteer. In \StageOne, the mean effort per agent was 263; in the shorter
\StageTwo it was 81.
%
\item{\noindent\bf ``Experience:''} The number of training images, $\experience$,
classified by a volunteer. In \StageOne, the mean experience per agent was 29;
in \StageTwo (where the training image frequency was set higher) it was 34.
%
\item{\noindent\bf ``Skill:''} The expectation value of the information gained
per classification (in bits) by that volunteer,  $\skill$ for subjects which
have lens probability 0.5 (\Aref{appendix:swap}). Random classifiers have
$\skill = 0.0$, while perfect classifiers have $\skill = 1.0$. All agents start
with $\skill = 0.0$. The skill of  an agent increases as training subjects are
classified, and the agent's estimates of its confusion matrix elements improve.
In \StageOne, the mean skill per agent was 0.04 bits; in  \StageTwo it was 0.05.
%
\item{\noindent\bf ``Contribution:''} The integrated skill over a volunteer's
{\it test subject} classification history, a quantity representative of the
total contribution to the project made by that volunteer (see the appendix for
more discussion of this quantity). The classifications of training images
determine the skill, while the classification of test images determines
contribution.  In \StageOne, the mean  contribution per agent was
34.9 bits; in \StageTwo it was 33.5.
%
\item{\noindent\bf ``Information:''} The actual total information $\information$
generated by the agent during the volunteer's classification activity. This
quantity depends on the value of each subject's lens probability when that
subject was presented to the volunteer (simply because information gain is
defined in terms of posterior relative to prior probabilities,
\Aref{appendix:swap}).  Because of this, we expect this quantity to be noisier
than the ``contribution'' defined above.
%
\end{description}

The leftmost column of \Fref{fig:crowd:cornerplot} shows how the last four of
these properties depends on the effort expended by the volunteers. As expected,
we see that experience is tightly correlated with effort, reflecting the design
of training images being presented throughout each stage (albeit at decreasing
frequency). We also see a strong correlation between effort and skill, which was
hoped for but not guaranteed: the more images the volunteers see, the better
able to contribute information they are.

The effort distribution shows two peaks, suggestive of two types of
participation.  The sharp spike at just a few images classified presumably
corresponds to visitors who only classify a few subjects before leaving the site
again. The broader hump contains people doing tens to hundreds of
classifications: the skill vs.\ experience panel of \Fref{fig:crowd:cornerplot}
shows this group to achieve a broad distribution of  skill, peaking at around
0.05 but with a long tail to higher values.

At high values of experience and effort, the skill is \emph{always high}. There
seem to be very few agents logging large numbers of classifications at low skill
(although there are one or two exceptions): almost all high effort
``super-users'' have high skill. These two properties are reflected in both the
contributions these volunteers make (third row) and the information they
generate (fourth row).

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}
\centering\includegraphics[width=0.9\linewidth]{sw-system-figs/crowd_contrib_cumul.png}
\caption{Cumulative distributions of the contributions made by the agents: 90\%
of the contribution was made by the highest contributing 1\% of the crowd at
\StageOne (blue), and the highest contributing  7\% of the crowd at \StageTwo
(orange). The \StageOne agents are shown in blue, the \StageTwo agents in
orange. ``Experienced volunteers'' classified 10 or more training subjects.}
\label{fig:crowd:cumulplot}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\Fref{fig:crowd:cornerplot} shows the \SW crowd to have quite broad
distributions of logarithmic effort, skill, and contribution. To better
quantify the contributions made by the volunteers, we show their cumulative
distribution on a linear scale in \Fref{fig:crowd:cumulplot}. This plot shows
clearly the importance of the hardest-working, most active volunteers: at
\StageOne,  1.0\% of the volunteers -- 375 people -- made 90\% of the
contribution.  At \StageTwo, where it was not possible to make as
many classifications before running out of subjects, 7.2\% of the volunteers
-- 141 people -- made 90\% of the contribution.

However, it is not the case that only these small groups were {\it capable} of
making large contributions. The cumulative distribution of agent skill is shown
in \Fref{fig:crowd:cumulskillplot}: these distributions are significantly
broader than the corresponding distributions of agent contribution, in
\Fref{fig:crowd:cumulplot}. The most skilled 20\% of agents only possess around
80\% of the skill at each stage. The inexperienced volunteers also possess a
significant fraction of the skill: the most skillful 20\% of experienced
volunteers (1824 people)  possess just 43\% of the total skill. The breadth of
the skill distributions suggests that  the high level of contribution made at
\SW by experienced volunteers is largely a matter of choice (or perhaps,
availability of time!). There were many other volunteers that  were skillful
enough to make large contributions -- they just didn't classify as many images.

@@

How fast does the \SW crowd classify subjects? Each agent records the timestamp
of each classification its volunteer makes; by measuring the time lags between
successive classifications we can make estimates of the crowd's classification
and contribution speed. We plot these two quantities for both \StageOne and
\StageTwo in \Fref{fig:results:speed}, normalizing the speed and time axes to
the respective totals. The fractional classification rates in each stage of the
survey fall off in approximately the same way, despite the factor of nearly 20
difference in crowd size. \StageOne (consisting of $\sim430,000$ subjects) was
completed in around 5000 hours (by some 37,000 participants), with
classification rates in the first few days averaging at $\sim10^4$ per hour.
This was stimulated by various forms of advertising (press releases, and emails
to registered Zooniverse users). The asymptotic classification rate was  around
ten times lower, at $\sim10^3$ per hour. Interestingly, the average skill was
found to be approximately constant over the lifetime of \StageOne, leading to a
contribution rate that tracks closely the classification rate. (A 10\% increase
in average skill was seen over the first 40 days, and a decrease of the same
amount in the last 40 days -- not enough to cause a significant difference
between classification and contribution rate behavior, but perhaps reflecting a
learning period at the start and a decrease in participation late on.) \StageTwo
(3700 subjects) was completed in around 600 hours by around 2000 participants,
with classification rates starting at $~\sim2000$ per hour and decaying to
$\sim100$ per hour.

@@

We now quantify the performance of the \SW system in terms of the recovery of
the training set images. At \StageOne, this set contains around 5712 simulated
lenses, and 450 duds; at \StageTwo, we used 152 simulated lenses and 201 duds.
\Fref{fig:results:sample:roc} shows receiver operating characteristic (ROC)
curves for CFHTLS \StageOne and \StageTwo. These plots show the true positive
rate (TPR, the number of sims correctly detected divided by the total number of
sims in the training set), and the false positive rate (FPR, the number of duds
incorrectly detected  divided by the total number of duds in the training set), both
for a given sample of detections defined by a particular probability threshold,
which varies along the curves.  In both stages, these curves show that true
positive rates of  around 90\% were achieved, at very low false positive rates.

For comparison we show the results of an analysis where the classifications of
training images were ignored, and none of the agents allowed to learn: the
agents were instead simply assigned initial values of their confusion matrices
of 0.75 for each element, which then remained constant. This set-up emulates a
very simple unweighted voting scheme, where all classifications are treated
equally.  In this case, the TPR remains under 80\% in \StageOne and 60\% in
\StageTwo, thus quantifying  the benefit of including training images and
allowing the agents to learn via their Bayesian updates.

When the agents are allowed to update their confusion matrices, the choice of
initial confusion matrix is not very important. The same 0.75 initial values
applied to normal, learning agents resulted in only a slightly lower TPR than
the default case, nevertheless indicating that initializing the system less
conservatively results in slightly worse performance.

The dot-dashed curves show the impact of the offline analysis. At \StageOne the
results are very similar to the online version that was actually run (solid
line). However, at \StageTwo there is marginal evidence of there being greater
benefit to doing the analysis offline (\Sref{sec:swap}, \Aref{appendix:swap}).
Over 85\% TPR is achieved at zero FPR in the offline analysis , while if one is
willing to accept a false positive rate of 5\%, the true positive rate rises to
over 95\%, showing that some of the sims that were missed in the online analysis
may be being recovered by doing the analysis offline. The same is true at
\StageOne, but to a lesser extent. Assuming Poisson statistics for the
fluctuations in the numbers of recovered lenses, the uncertainty in the measured
\StageTwo TPR values is around 8\%, but the online and offline samples are
highly correlated, such that the uncertainty on the difference between the ROC
curves is somewhat less than this. Still, a larger validation set is needed to
test these algorithmic choices more rigorously. At \StageOne, high TPR can be
measured to better than 1\%.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}
\begin{minipage}{0.45\linewidth}
  \centering\includegraphics[width=\linewidth]{sw-system-figs/stage1_ROC.png}
\end{minipage}\hfill
\begin{minipage}{0.45\linewidth}
  \centering\includegraphics[width=\linewidth]{sw-system-figs/stage2_ROC.png}
\end{minipage}
\caption{Receiver operating characteristic curves for the \SW system, using
the CFHTLS training set. Left: \StageOne, right: \StageTwo. Insets show a
magnified view of the top lefthand corner of each plot. Linestyles illustrate
the agent properties (initial confusion matrix elements, learning or not)
discussed in the text, as well as the difference between the online and offline
analyses. The \StageTwo sample was defined using the online \StageOne results
(solid blue curve), while the offline analysis was chosen for the final
\StageTwo results (dot-dashed orange curve). }
\label{fig:results:sample:roc}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

Adopting the online \StageOne analysis, and the offline \StageTwo analysis, we
show in \Fref{fig:results:sample:CP} a plot of the more familiar (to
astronomers) quantities of completeness versus purity, again for
the two stages. As in \Fref{fig:results:sample:roc}, the detection threshold
varies along the curves. Completeness is defined as the number of correctly
detected sims divided by the total number of sims in the training set, while
purity is the number of correct detections divided by the total number of
detections.\footnote{The completeness is equivalent to the TPR and is also
known elsewhere as the ``recall.''  The purity is also known as the
``precision.''} If the training set samples from the same systems as the test
set, then the completeness of the training set will be equivalent to the
completeness of the test set. The purity depends on the proportion of sims to
duds, and so the purity of the test set must be approximated by rescaling the
training set to the expected proportion of lens systems to not-lens systems in
the survey. First we compute the expected number of false positives by
multiplying the FPR by the expected number of non-lenses in the survey. Then
we multiply the TPR by the expected number of lenses in the survey, to get the
expected number of true positives. The sum of the true positives and the false
positives gives the expected sample size; dividing the expected number of true
positives by this sample size gives the purity. Note that the completeness is
invariant to this transformation.
The \StageOne curves are truncated by the retirement of subjects in this phase,
which sets the minimum size of this sample. We see from the solid blue curve
that over 90\% completeness was reached, albeit in a sample with around 20\%
purity.

Does this performance level vary between the different types of gravitational
lens? To investigate the completeness to the three different types of lens in
the training set, we repeated the same procedure but now considering only the
detections of a certain kind of lens and of the non-lenses in the training set.
We estimate the expected number of lenses and non-lens false positives by
dividing the lens and dud sets into equal fractions. The lensed quasar part of
the training set yielded the highest completeness, suggesting that these were
the easiest sims to spot. The lensed galaxies were recovered at the lowest
completeness, likely due to the difficulty  of separating the lens and source
galaxy light.

At \StageTwo, where no retirement was carried out, it was possible to reach
100\% purity: the knee of the curve is at just under 90\% completeness. However,
the purity decreases rapidly if higher completeness than this is sought. The
optimal sample in this simulated lens search experiment would have been
constructed with a threshold value of $\pr(\LENS|C,T) > 0.47$. At 100\% purity
and 90\% completeness, it would have contained around 89 lens candidates.

% TP + FN ~ 2e-4 * 430000 ~ 100 ~ TP/C ; so TP ~ 89 candidates

@@

We investigated the source of the incompleteness and impurity visible in
\Fref{fig:results:sample:CP}, by examining the \StageTwo false negatives and
false positives, and their behaviour as they are classified using the online
analysis trajectory plots introduced in \Sref{sec:swap}
(\Fref{fig:swap:subject-trajectories}).
\Fref{fig:discuss:performance:trajectories} shows 2 example simulated lenses
that were missed ($\pr(\LENS|C,T) < 10^{-5}$) by the \SW system, and 2 example
non-lenses that were incorrectly flagged as candidates ($\pr(\LENS|C,T) >
0.95$) by the \SW system. While the final \StageTwo analysis was done offline,
these trajectory plots still serve to illustrate the approximate
classification histories of the subjects.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{table*}
\begin{center}
\caption{Total crowd and subject sample properties from the CFHTLS project.}
\label{tab:crowd:contributions}
\begin{tabular}{cccccccc}
  \hline
  % \hline {Stage} & Subjects & Contribution                          & Agents & Skill      & Classifications          & Candidates & Information \\
  %                & $\Ns$    & $\sum_k^{\Nv} \contribution_k$ (bits) & $\Nv$  & $\sum_k^{\Nv} \skill_k$ (bits) & $\sum_k^{\Nv} \thiseffort$ & $\Ncands$  & $\sum_j^{\Ns}\sum_k^{\Nv} \information_{j,k}$ (bits) \\
  % \hline
  %           1    & $427064$ & $1292016.3$ & $36982$ & $1471.9$ & $10802125$ & $3368$ & $91122.6$ \\
  %           2    & $3679$   &   $21895.8$ &  $1964$ &  $102.4$ &   $224745$ &   $90$ &  $1640.4$ \\
  \hline {Stage} & Subjects & Contribution                          & Agents & Skill      & Classifications          & Candidates & Information \\
                           & $\Ns$    & $\sum_k^{\Nv} \contribution_k$ (bits) & $\Nv$  & $\sum_k^{\Nv} \skill_k$ (bits) & $\sum_k^{\Nv} \thiseffort$ & $\Ncands$  & $\sum_j^{\Ns}\sum_k^{\Nv} \information_{j,k}$ (bits) \\
            \hline
                      1    & $427064$ & $1292016.3$ & $36982$ & $1471.9$ & $10802125$ & $3368$ & $91122.6$ \\
                      2    & $3679$   &   $21895.8$ &  $1964$ &  $102.4$ &   $224745$ &   $90$ &  $1640.4$ \\
  \hline \hline
\end{tabular}
\medskip\\
\end{center}
\end{table*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

Finally, we comment on the size of the first \SW crowd, and how the system
might be scaled up for future surveys. In \Sref{sec:results:crowd} and
\Tref{tab:crowd:contributions}, a rough picture emerged for the \SW crowd of
it containing a few $10^4$ volunteers, with a few $10^3$ achieving
considerable skill, and a few $10^2$ having the time to make a significant
contribution. Slightly more quantitively, we might note that  the total skill
of the crowd, computed by summing the skill of all the agents, is a measure of
the effective crowd size, in the sense that a crowd of perfect classifiers
would be of this size. By this measure,the \StageOne crowd was equivalent to a
team of 1470 perfect classifiers, while the \StageTwo crowd was equivalent to a
team of 102 perfect classifiers. With this same crowd, we can see that surveys
providing a few $10^4$ subjects would be completed quickly, if the high
contribution rate of the current crowd were to be repeated.
